Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2017-10-17 TACAS2018/paper.tex
sec 6.4

We may now use this limit to express a constraint in terms of the
coefficients for our synthesis process.  Let

@@

P=\prod_{i=0}^p (s-\lambda_i)=\sum_{j=0}^p c_js^j.

@@

We use Jury's criterion to limit $|\lambda_i| \leq 1$.  Let us now define a

@@

to $P'=\prod_{i=0}^p (s-\lambda_i')=\sum_{j=0}^p c_j's^j$ where $c_j'$ are
unknown.  However, if we replace for $\lambda_i$, we obtain

@@

where all members are known, we may now synthesise coefficients that ensure
the eigenvalues are smaller than a desired magnitude, thus ensuring that the
settling time is too.

>>>>

We now use this limit to express a constraint in terms of the
coefficients of the characteristic polynomial.  Let this
polynomial be:

@@

P(s)=\prod_{i=0}^p (s-\lambda_i)=\sum_{j=0}^p c_js^j.

@@

%We can use Jury's criterion to limit $|\lambda_i| \leq 1$.
Let us now define a

@@

to $P'(s)=\prod_{i=0}^p (s-\lambda_i')=\sum_{j=0}^p c_j's^j$ where $c_j'$ are
unknown.  By replacing $\lambda_i$, we obtain

@@

where all members are known. Thus, we can ensure that the settling time is smaller than
a certain magnitude by ensuring that 
the eigenvalues are smaller too (which we can do with Jury's criterion).
